---
title: "CoV-FISH-MS_Figure2"
author: "Jeff Lee"
date: "20/03/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Environment
```{r}
library(tidyverse)
library(hrbrthemes)
library(patchwork)
library(rstatix)
library(ggridges)
library(janitor)
library(ggbeeswarm)

```

# N protein 
## gRNA line profiles 
```{r}
line_profile_data <- read_csv("./Data/Figure2/N-protein_gRNA_line-profiles.csv")

ggplot(line_profile_data) +
  geom_line(aes(x = Distance, y = normalised, colour = signal),
            size = 0.5) +
  scale_colour_manual(values = c("#8fd175", "#d18975")) +
  labs(title = "Fluorescence profile",
       x = "Distance (µm)",
       y = "Normalised \nfluorescence") +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        legend.position = "bottom",
        axis.line = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        legend.title = element_blank()) -> plot1

plot1

```

## N protein overlap with gRNA and sgRNA 
```{r}
# Import data
N_overlap <- read_csv("./Data/Figure2/p_NProtein-overlap_random.csv") %>%
  filter(str_detect(data_type, "Observed")) %>%
  mutate(data_type = str_remove(data_type, " Observed"))

# Get mean labels
N_overlap_anno <- N_overlap %>%
  group_by(data_type) %>%
  summarise(mean = mean(p_NCed_stringent)) %>%
  ungroup() %>%
  mutate(label = paste0(round(mean, 1), "%"))

# Statistics
N_overlap %>% group_by(data_type) %>% shapiro_test(p_NCed_stringent) # normal
star <- N_overlap %>% t_test(p_NCed_stringent ~ data_type) %>% add_significance() %>% pull(p.signif)
pval <- N_overlap %>% t_test(p_NCed_stringent ~ data_type) %>% add_significance() %>% pull(p) 
stat_anno <- paste0(star, "\np=", pval)

# Plot 
N_overlap %>%
  mutate(data_type = fct_rev(data_type)) %>%
  ggplot(aes(x = data_type, y = p_NCed_stringent, fill = data_type)) +
  geom_bar(stat = "summary", width = 0.75) +
  geom_linerange(stat = "summary", fun.data = "mean_sdl", 
                 fun.args = list(mult = 1), size = 0.4) +
  scale_y_continuous(breaks = seq(0, 100, by = 20),
                     limits = c(0, 100)) + 
  scale_fill_manual(values = c("#d175b8", "#8fd175")) +
  geom_label(data = N_overlap_anno,
             aes(x = data_type, y = mean + 13, label = label), 
             size = 1.5, label.padding = unit(0.15, "lines"), label.size = 0.1,
             inherit.aes = FALSE) + 
  labs(title = "N protein colocalisation",
       x = "", 
       y = "% of molecules") +
  theme_classic(base_size = 7) + 
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.line = element_blank(),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  annotate(geom = "text", x = 1.5, y = 90, label = stat_anno, size = 1.5, colour = "gray10") +
  coord_flip() -> plot2

# patchwork
plot1 + plot2

pdf("./Plots/N-protein_gRNA_overlap.pdf",
    width = 11.1/2.54, height = 4.4/2.54)
print(plot1 + plot2)
dev.off()

```


# J2 comparison with smFISH
## J2 smFISH comparison data
```{r}
# Import data 
dsRNA_infection <- read_csv("./Data/Figure2/p-infection_J2_positive.csv") %>%
  mutate(Time = case_when(condition == "MOCK" ~ "Mock",
                          TRUE ~ Time))

smFISH_infection <- read_csv("./Data/Figure2/p-infection_smFISH_positive_cells.csv") %>%
  mutate(Time = case_when(condition == "MOCK" ~ "Mock",
                          TRUE ~ Time))


dsRNA_intensity <- read_csv("./Data/Figure2/Quantification_J2_intensity.csv") %>%
  mutate(time.adj = as.character(time.adj)) %>%
  mutate(hours_post_infection = case_when(condition == "INF" ~ paste0(time.adj, "hpi"),
                                          condition == "MOCK" ~ "Mock"))

smFISH_count <- read_csv("./Data/Figure2/Quantification_smFISH_count.csv") %>%
  mutate(time.adj = as.character(time.adj)) %>%
  mutate(hours_post_infection = case_when(condition == "INF" ~ paste0(time.adj, "hpi"),
                                          condition == "MOCK" ~ "Mock"))
```


## Comparison plots
```{r}
# * * * * Plots
dsRNA_infection %>%
  mutate(Time = as_factor(Time)) %>%
  mutate(Time = fct_relevel(Time, c("Mock", "2hpi", "6hpi"))) %>%
  ggplot(aes(x = Time, y = p.infected, fill = Time)) +
  geom_bar(stat = "summary", width = 0.75) +
  geom_linerange(stat = "summary", fun.data = "mean_sdl", 
                 fun.args = list(mult = 1), size = 0.4) +
  scale_y_continuous(breaks = seq(0, 100, by = 20),
                     limits = c(0, 100)) + 
  scale_fill_manual(values = c("#d175b8", "#9c4c85","#6a2656")) +
  labs(title = "dsRNA (J2)",
       x = "Hours post infection", 
       y = "% cells above 95% percentile \n Mock fluorescence") +
  theme_classic(base_size = 7) + 
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) -> p1

smFISH_infection %>%
  mutate(Time = as_factor(Time)) %>%
  mutate(Time = fct_relevel(Time, c("Mock", "2hpi", "6hpi"))) %>%
  ggplot(aes(x = Time, y = p.infected, fill = Time)) +
  geom_bar(stat = "summary", width = 0.75) +
  geom_linerange(stat = "summary", fun.data = "mean_sdl", 
                 fun.args = list(mult = 1), size = 0.4) +
  scale_y_continuous(breaks = seq(0, 100, by = 20),
                     limits = c(0, 100)) + 
  scale_fill_manual(values = c("#8fd175", "#659e58","#204121")) +
  labs(title = "smFISH gRNA",
       x = "Hours post infection", 
       y = "% fluorescence positive cells") +
  theme_classic(base_size = 7) + 
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) -> p2

dsRNA_intensity %>%
  ggplot(aes(x = factor(hours_post_infection, levels = c("Mock", "2hpi", "6hpi")), 
             y = dsRNA_density, colour = hours_post_infection)) +
  geom_quasirandom(width = 0.4, size = 0.25, alpha = 0.5) +
  geom_hline(yintercept = 1, alpha = 0.1, size = 0.25) +
  scale_y_continuous(limits = c(0, 7)) +
  # scale_y_log10(limits = c(0.4, 1e2),
  #               labels = trans_format("log10", math_format(10^.x))) +
  scale_colour_manual(values = c("#9c4c85","#6a2656", "#d175b8")) +
  labs(title = "J2 intensity", 
       x = "Hours post infection",
       y = "Normalised fluorescence density") +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.title.x = element_blank(),
        axis.line = element_blank(),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5)) -> p3

smFISH_count %>%
  mutate(total_count = total_count + 1) %>%
  ggplot(aes(x = factor(hours_post_infection, levels = c("Mock", "2hpi", "6hpi")), 
             y = total_count, colour = hours_post_infection)) +
  geom_quasirandom(width = 0.4, size = 0.25, alpha = 0.25) +
  geom_hline(yintercept = 1, alpha = 0.1, size = 0.25) +
  scale_y_log10(limits = c(1, 1e5),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_colour_manual(values = c("#659e58","#204121", "#8fd175")) +
  labs(title = "smFISH gRNA count", 
       x = "Hours post infection",
       y = "RNA count + 1 (log10)") +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.title.x = element_blank(),
        axis.line = element_blank(),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5)) -> p4

# Patchwork
(p1 + p2) / (p3 + p4)

# Export 
pdf("./Plots/dsRNA-comparison.pdf",
    width = 8/2.54, height = 8.25/2.54)
print((p1 + p2) / (p3 + p4))
dev.off()

```

## Statistics 

### Percentage infection statistics 

```{r}
# * * * * * J2 statistics 

# Normality
dsRNA_infection %>%
  group_by(Time) %>%
  shapiro_test(p.infected) # normal

# ANOVA
dsRNA_infection %>%
  anova_test(p.infected ~ Time) # significant

# Tukey HSD
dsRNA_infection %>%
  tukey_hsd(p.infected ~ Time)

# * * * * * smFISH statistics

# Normality
smFISH_infection %>%
  group_by(Time) %>%
  shapiro_test(p.infected) # Not normal

# Kruskal
smFISH_infection %>%
  kruskal_test(p.infected ~ Time) # significant

# Dunn
smFISH_infection %>%
  dunn_test(p.infected ~ Time)


```


### Quantification statistics 

```{r}
# * * * * *  J2 statistics

# Normality
dsRNA_intensity %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(dsRNA_density),
            median = median(dsRNA_density)) %>% ungroup() %>%
  group_by(hours_post_infection) %>%
  shapiro_test(mean) # Normal

# ANOVA
dsRNA_intensity %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(dsRNA_density),
            median = median(dsRNA_density)) %>% ungroup() %>%
  anova_test(mean ~ hours_post_infection) # Not significant 


# * * * * * smFISH statistics 

# Normality 
smFISH_count %>%
  filter(hours_post_infection != "Mock") %>%
  mutate(total_count_log = log10(total_count + 1)) %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(total_count_log),
            median = median(total_count_log)) %>% ungroup() %>%
  group_by(hours_post_infection) %>%
  shapiro_test(mean) # Normal 

# ANOVA
smFISH_count %>%
  mutate(total_count_log = log10(total_count + 1)) %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(total_count_log),
            median = median(total_count_log)) %>% ungroup() %>%
  anova_test(mean ~ hours_post_infection) # Significant 

# Tukey HSD
smFISH_count %>%
  mutate(total_count_log = log10(total_count + 1)) %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(total_count_log),
            median = median(total_count_log)) %>% ungroup() %>%
  tukey_hsd(mean ~ hours_post_infection,
            p.adjust.method = "holm")

smFISH_count %>%
  mutate(total_count_log = log10(total_count + 1)) %>%
  group_by(hours_post_infection, repeat_exp) %>%
  summarise(mean = mean(total_count_log),
            median = median(total_count_log)) %>% ungroup() %>%
  t_test(mean ~ hours_post_infection)



```


# SUPPLEMENTARY

## SARS-CoV-2 RNA dispersion statistics 
For comparing subcellular distribution of SARS-CoV-2 RNA species. RDI calculator was used on thresholded images to calculated RNA dispersion indices. 

Raw images were max-projected and thresholded: DAPI - Huang2, CellMask - Huang, smFISH - Max Entropy or Li.
Thresholded images were padded (so that the cells are not touching the edge) with empy pixels. 
Resulting images were fed into RDI calculator without background subtraction. 

```{r}
# * * * * * Import dataframe
RDI_raw <- read_csv("./Data/Figure2/RNA-dispersion-index_Vero_6hpi_RAW_DATA.csv") 

RDI_tidy <- RDI_raw %>%
  clean_names() %>%
  dplyr::select(contains("periph"), contains("polarization"), contains("dispersion")) %>%
  pivot_longer(cols = everything(),
               names_to = "data_type",
               values_to = "index") %>%
  mutate(species = if_else(str_detect(data_type, "localized"), "ORFN", "gRNA")) %>%
  mutate(RDI_type = case_when(
    str_detect(data_type, "periph") ~ "Peripheral Distribution Index",
    str_detect(data_type, "polarization") ~ "Polarisation Index",
    str_detect(data_type, "dispersion") ~ "Dispersion Index"
  ))

# * * * * * Stats

## Normality test
RDI_tidy %>%
  group_by(RDI_type, species) %>%
  shapiro_test(index)

## 
RDI_tidy %>%
  group_by(RDI_type) %>%
  wilcox_test(index ~ species)

# * * * * * Plot
colours <- c("#8fd175", "#d175b8")

RDI_tidy %>%
  filter(RDI_type != "Polarisation Index") %>%
  ggplot(aes(x = species, y = index, colour = species)) +
  geom_quasirandom(bandwidth = 0.2) +
  scale_colour_manual(values = colours) + 
  facet_wrap(~RDI_type)
  







```


## N protein co-localisation with sg/gRNAs
For comparing N-protein intensities in sgRNA/gRNA ellipsoids of Observed and Random distributed RNA for use with thresholding N co-localisation + compare N co-localisation of gRNA and sgRNA

```{r}
# * * * * * Read data
N_int_raw <- read_csv("./Data/Figure2/NProtein-overlap_intensity.csv") %>%
  mutate(simulation = if_else(str_detect(data_type, "Observed"), "Observed", "Random"))

# * * * * * Density plot
colours <- c("#8fd175", "#d175b8")

N_int_raw %>% 
  ggplot(aes(x = IntegratedDensity, y = stat(ndensity), 
             colour = species, fill = species, alpha = simulation)) + 
  geom_density() + 
  scale_x_log10() +
  scale_colour_manual(values = colours) + 
  scale_fill_manual(values = colours) +
  scale_alpha_manual(values = c(0.8, 0.3))

# * * * * * ggridge plot
colours <- c("#8fd175", "#d175b8")
order <- c("gRNA\nObserved", "sgRNA\nObserved", "gRNA\nRandom", "sgRNA\nRandom")

N_int_raw %>% 
  filter(IntegratedDensity > 0) %>%
  mutate(data_type = str_replace(data_type, " ", "\n")) %>%
  mutate(data_type = fct_relevel(data_type, rev(order))) %>%
  ggplot(aes(x = IntegratedDensity, 
             y = data_type, 
             colour = species, fill = species, alpha = simulation)) + 
  geom_vline(xintercept = 1500, size = 0.3, colour = "gray60", linetype = "dashed") +
  geom_density_ridges(aes(height = stat(ndensity)),
                       scale = 1.2, bandwidth = 0.02, size = 0.4) + 
  scale_x_log10(labels = trans_format("log10", math_format(10^.x))) +
  scale_colour_manual(values = colours) + 
  scale_fill_manual(values = colours) +
  scale_alpha_manual(values = c(0.7, 0.2)) +
  labs(title = "SARS-CoV-2 RNA species N protein co-localisation", 
       x = "Colocalised N protein voxel intensity (AU)",
       y = "Density distribution",
       fill = "",
       colour = "") +
  theme_classic(base_size = 8) +
  theme(plot.title = element_text(hjust = 0.5, size = 8),
        axis.text.y = element_text(size = 8, face = "bold"),
        axis.line = element_blank(),
        legend.position = "right",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5)) +
  guides(alpha = "none") -> N_overlap_ridges

N_overlap_ridges


pdf("./Plots/N_overlap_ridges.pdf",
    width = 4.75, height = 3)
print(N_overlap_ridges)
dev.off()



```





















