---
title: "CoV-FISH-MS_Figure5"
author: "Jeff Lee"
date: "24/03/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# ENVIRONMENT

```{r}
library(tidyverse)
library(ggbeeswarm)
library(hrbrthemes)
library(patchwork)
library(scales)
library(rstatix)
library(ggridges)

```

# VICTORIA vs. B.1.1.7 smFISH

## Infection rate and viral entry
```{r}
# * * * * * % infection
# Prepare data
RNA_df <- read_csv("./Data/Figure5/Data_summary_threshold_150.csv") %>%
  dplyr::select(c("File" = file_name, time, "Virus" = strain, "condition" = treatment, everything(), -X1)) %>%
  mutate(Virus = case_when(
    Virus == "B117" ~ "B.1.1.7",
    Virus == "Vic" ~ "Victoria",
    Virus == "None" ~ "Mock")) %>%
  mutate(condition = case_when(
    condition == "INF" ~ "Untreated",
    TRUE ~ condition)) %>%
  mutate(time = case_when(
    time == 2 ~ "2 hpi",
    time == 6 ~ "6 hpi",
    time == 8 ~ "8 hpi",
    time == 24 ~ "24 hpi")) %>%
  mutate(repeat_exp = case_when(
    str_detect(File, "R1") ~ "R1",
    str_detect(File, "R2") ~ "R2",
    str_detect(File, "R3") ~ "R3"
  ))

p_infection <- RNA_df %>% 
  filter(Virus != "Mock" & condition == "Untreated" & time == "2 hpi") %>%
  mutate(File = str_replace(File, "cell_[:alnum:]", "")) %>%
  group_by(File, Virus, repeat_exp) %>%
  summarise(n_cell = n(),
            n_inf = sum(ch4_total_vRNAs > 4),
            p_inf = sum(ch4_total_vRNAs > 4)/n()*100) %>%
  ungroup() %>%
  mutate(Virus = fct_rev(Virus)) %>%
  group_by(Virus, repeat_exp) %>% summarise(mean_p_inf = mean(p_inf)) %>% 
  ungroup()

# Statistics
p_infection %>% group_by(Virus) %>% shapiro_test(mean_p_inf)
p_inf <- p_infection %>% t_test(mean_p_inf ~ Virus) %>% pull(p)
p_anno_inf <- paste0("p=", p_inf)

# * * * * * Viral entry
# Prepare data 
RNA_df_2hpi <- RNA_df %>% filter(time == "2 hpi") %>% filter(Virus != "Mock") %>%
  filter(ch4_total_vRNAs > 1) %>%
  mutate(Virus = fct_rev(Virus)) %>%
  mutate(colour_factor = paste0(Virus, "-", repeat_exp))

# Statistics 
RNA_df_2hpi %>% group_by(Virus, repeat_exp) %>% summarise(mean = mean(ch4_total_vRNAs)) %>%
  shapiro_test(mean)
RNA_df_2hpi %>% group_by(Virus, repeat_exp) %>% summarise(mean = mean(ch4_total_vRNAs)) %>%
  ungroup() %>% t_test(mean ~ Virus) %>% pull(p) -> p_entry

# Annotation
RNA_df_2hpi_anno <- RNA_df_2hpi %>% group_by(Virus) %>% 
  summarise(mean = mean(ch4_total_vRNAs)) %>% 
  ungroup() %>%
  mutate(mean = round(mean, 1))
p_anno_entry <- paste0("p=", p_entry)


# * * * * *  Plots
# % infection plot
p_infection %>%
  ggplot(aes(x = Virus, y = mean_p_inf, fill = Virus)) +
  geom_bar(stat = "summary",
           width = 0.5) +
  geom_linerange(stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1),
                 size = 0.5) +
  scale_fill_manual(values = c("#f9ab38", "#5672be")) + 
  labs(title = "% infected cells",
       x = "",
       y = "% cells per image") + 
  theme_classic(base_size = 7) +
  theme(plot.title       = element_text(hjust = 0.5),
        legend.title     = element_blank(),
        legend.key.size  = unit(0.2, "cm"),
        legend.position  = "none", 
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  annotate(geom = "text", label = p_anno_inf, size = 2, alpha = 0.75,
           x = 1.5, y = 100) -> p1_2hpi

# Viral entry plot
RNA_df_2hpi %>%
  ggplot(aes(x = Virus, y = ch4_total_vRNAs, colour = colour_factor)) +
  geom_beeswarm(cex = 0.8, alpha = 0.15, size = 0.75, stroke = 0,
                priority = "random") +
  geom_point(stat = "summary", position = position_dodge(width = 0.1), 
             size = 1.5, alpha = 1) +
  geom_label(data = RNA_df_2hpi_anno, 
             aes(x = Virus, y = 150, label = mean), 
             inherit.aes = FALSE,label.padding = unit(0.1, "lines"), size = 2) +
  scale_y_continuous(limits = c(0, 200)) +
  scale_colour_manual(
    values = c("#5672be", "#2f416f", "#0d152a", "#f9ab38", "#c39050", "#8b7660")) +
  labs(title = "Viral entry (2hpi)",
       x = "",
       y = "(+)ve gRNA total count") +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        legend.position = "none",
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  annotate(geom = "text", label = p_anno_entry, size = 2, alpha = 0.75,
           x = 1.5, y = 190) -> p2_2hpi

# Patchwork
(p2_2hpi + p1_2hpi)

## Export
pdf("./Plots/Vero-variant-infection-entry.pdf",
    width = 8.5/2.54, height = 4.2/2.54)
print((p2_2hpi + p1_2hpi))
dev.off()


```

## Total RNA

```{r}
# * * * * * Data

RNA_df_total <- read_csv("./Data/Figure5/CF10_JL_20210629.csv") %>%
  mutate(gRNA_log = log10(total_vRNAs_gRNA))

RNA_df_total %>%
  group_by(time, strain) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  arrange(strain)

# * * * * * Statistics 

## 2 hpi
RNA_df_total %>% group_by(time, condition, strain, repeat_exp) %>%
  filter(time == "2hpi") %>%
  filter(total_vRNAs_gRNA > 0) %>%
  summarise(gRNA_mean = mean(gRNA_log, na.rm = TRUE)) %>% ungroup() %>%
  group_by(time, condition, strain) %>%
  shapiro_test(gRNA_mean) # normal

RNA_df_total %>% group_by(time, condition, strain, repeat_exp) %>%
  filter(time == "2hpi") %>%
  filter(total_vRNAs_gRNA > 0) %>%
  summarise(gRNA_mean = mean(gRNA_log, na.rm = TRUE)) %>% ungroup() %>%
  group_by(time, condition) %>%
  t_test(gRNA_mean ~ strain)

## 6-8 hpi: KS statistics test function
do_ks_test <- function(time, condition, test){
  vic <- RNA_df_total[RNA_df_total$time == time & RNA_df_total$condition == condition, ] %>% filter(strain == "Victoria") %>%
    pull(test)
  b17 <- RNA_df_total[RNA_df_total$time == time & RNA_df_total$condition == condition, ] %>% filter(strain == "B.1.1.7") %>%
    pull(test)
  ks.test(vic, b17, alternative = "two.sided") %>% tidy() %>% add_significance()
}

## Do tests
do_ks_test(time = "6hpi", condition = "Untreated", test = "total_vRNAs_gRNA")
do_ks_test(time = "8hpi", condition = "Untreated", test = "total_vRNAs_gRNA")
do_ks_test(time = "6hpi", condition = "RDV", test = "total_vRNAs_gRNA")
do_ks_test(time = "8hpi", condition = "RDV", test = "total_vRNAs_gRNA")

# * * * * * Plot
set.seed(13)
rows <- sample(nrow(RNA_df_total))
RNA_df_total_plot <- RNA_df_total[rows, ]

RNA_df_total_plot %>%
  mutate(condition = fct_rev(condition)) %>%
  mutate(strain = fct_rev(strain)) %>%
  ggplot(aes(x = total_vRNAs_sgRNA, y = total_vRNAs_gRNA, colour = strain, alpha = strain)) +
  geom_point(size = 1, stroke = 0) +
  geom_vline(xintercept = 100000, linetype = "dotted", alpha = 0.5, size = 0.5) +
  geom_hline(yintercept = 100000, linetype = "dotted", alpha = 0.5, size = 0.5) +
  scale_colour_manual(values = c("#f9ab38", "#5672be")) +
  scale_alpha_manual(values = c(0.8, 0.5)) +
  scale_x_log10(limits = c(1e0, 1e7),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_log10(limits = c(1e0, 1e7),
                labels = trans_format("log10", math_format(10^.x))) +
  labs(title = "Total viral RNA count per cell",
       x = "sgRNA count (Log)",
       y = "gRNA count (Log)") + 
  facet_grid(condition ~ time) + 
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position  = c(0.07, 0.9),
        legend.background = element_blank(),
        legend.direction = "vertical",
        legend.title = element_blank(),
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) -> FACS

## Export
pdf("./Plots/Vero-variant_FACS_plot.pdf",
    width = 11/2.54, height = 7.9/2.54)
print(FACS)
dev.off()


```

## Viral factory number

```{r}
## Stat
RNA_df_total %>%
  group_by(condition, time, strain) %>%
  shapiro_test(repSites_gRNA)

RNA_df_total %>%
  group_by(condition, time) %>%
  wilcox_test(repSites_gRNA ~ strain) %>% add_significance()


## Plot
RNA_df_total %>%
  mutate(colour_arg = paste0(strain, " + " , condition)) %>%
  mutate(colour_arg = fct_rev(colour_arg)) %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = time, y = repSites_gRNA, colour = colour_arg)) +
  geom_pointrange(stat = "summary", fun.data = "mean_se", fun.args = list(mult = 1),
                  size = 0.5) +
  geom_line(aes(group = strain), stat = "summary",
            size = 0.5, alpha = 0.5) +
  scale_colour_manual(values = c("#f9ab38", "#f9d275", "#5672be", "#b4dded")) + 
  labs(title = "Number of viral factories per cell",
       x = "",
       y = "Count") +
  theme_classic(base_size = 7) + 
  facet_wrap(~condition) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        legend.position = c(0.75, 0.8),
        legend.background = element_blank(),
        legend.key.size = unit(0.3 ,"cm"),  
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) -> vfactory

vfactory

pdf("./Plots/Vero-variant_vfactory.pdf",
    width = 7.95/2.54, height = 4.6/2.54)
print(vfactory)
dev.off()


```

## Viral factory content

```{r}
## Stat
RNA_df_total %>%
  group_by(time, condition) %>%
  wilcox_test(content ~ strain) %>% add_significance() %>%
  arrange(desc(condition), time)

## Plot
RNA_df_total %>%
  mutate(condition = fct_rev(condition)) %>%
  mutate(strain = fct_rev(strain)) %>%
  mutate(time = fct_rev(time)) %>%
  ggplot(aes(x = content, y = time, colour = strain, fill = strain)) +
  geom_density_ridges(aes(height = stat(ndensity)), 
                      alpha = 0.4, size = 0.3, scale = 1.3, bandwidth = 0.16,
                      jittered_points = TRUE, point_shape = "|", point_size = 2.5,
                      position = position_points_jitter(height = 0)) +
  scale_fill_manual(values = c("#f9ab38", "#5672be")) + 
  scale_colour_manual(values = c("#f9ab38", "#5672be")) +
  scale_x_log10(labels = trans_format("log10", math_format(10^.x))) +
  labs(title = "Viral factory content",
       x = "Number of gRNA in viral factories per cell (Log)",
       y = "Density (at hours post infection)") +
  facet_wrap(~ condition) +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = c(0.25, 0.07),
        legend.direction = "horizontal",
        legend.key.size = unit(0.3 ,"cm"),  
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) -> vf_content

vf_content

pdf("./Plots/Vero-variant_vfactory_content.pdf",
    width = 11/2.54, height = 6/2.54)
print(vf_content)
dev.off()


```

## sgRNA ratio - per hpi

```{r}
## Stat
RNA_df_total %>%
  filter(ratio != Inf) %>%
  group_by(time, condition) %>%
  wilcox_test(ratio ~ strain) %>% add_significance() %>%
  arrange(condition, time)

## Plot
RNA_df_total %>%
  mutate(strain = fct_rev(strain))  %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = as.factor(time), y = ratio, colour = strain)) +
  geom_point(position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75),
            size = 0.65, alpha = 0.3, stroke = 0.1) +
  geom_pointrange(aes(x = as.factor(time), y = ratio, group = strain),
                  stat = "summary", position = position_dodge(width = 0.75), 
                  size = 0.3, colour = "gray50",
                  inherit.aes = FALSE, show.legend = FALSE) +
  geom_line(aes(group = strain), stat = "summary", size = 0.6, 
            alpha = 1) +
  geom_hline(yintercept = 1, linetype = "dashed",
             size = 0.5, colour = "gray75") + 
  coord_cartesian(ylim = c(0, 30)) + 
  labs(title = "sgRNA/gRNA ratio (by hpi)",
       x = "Hours post infection",
       y = "sgRNA/gRNA ratio") +
  scale_colour_manual(values = c("#f9ab38", "#5672be")) + 
  facet_wrap(~ condition) +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.line = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.8),
        legend.background = element_blank(),
        legend.direction = "horizontal",
        legend.key.size = unit(0.3, "cm"),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  guides(color = guide_legend(override.aes = list(size = 2, alpha = 1))) -> ratio_hpi


pdf("./Plots/Vero-variant_ratio-hpi.pdf",
    width = 8.3/2.54, height = 5.92/2.54)
print(ratio_hpi)
dev.off()

```

## sgRNA ratio - by classification

```{r}
## Data
RNA_df_rc <- RNA_df_total %>%
  mutate(classification = case_when(
    total_vRNAs_gRNA <= 100 ~ "Partially resistant",
    total_vRNAs_gRNA > 100 & total_vRNAs_gRNA < 100000 ~ "Permissive",
    total_vRNAs_gRNA >= 100000 ~ "Super-permissive"))

## Stat
RNA_df_rc %>%
  group_by(classification, condition) %>%
  wilcox_test(ratio ~ strain) %>% add_significance() %>%
  arrange(condition)

## Plot
RNA_df_rc %>%
  mutate(classification = fct_relevel(classification, c("Partially resistant", "Permissive", "Super-permissive"))) %>%
  mutate(strain = fct_rev(strain))  %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = as.factor(classification), y = ratio, colour = strain)) +
  geom_point(position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.75),
            size = 0.8, alpha = 0.3, stroke = 0.1) +
  geom_pointrange(aes(x = as.factor(classification), y = ratio, group = strain),
                  stat = "summary", position = position_dodge(width = 0.75), 
                  size = 0.3, colour = "gray50",
                  inherit.aes = FALSE, show.legend = FALSE) +
  geom_hline(yintercept = 1, linetype = "dashed",
             size = 0.5, colour = "gray75") + 
  coord_cartesian(ylim = c(0, 30)) + 
  labs(title = "sgRNA/gRNA ratio by gRNA burden",
       x = "",
       y = "sgRNA/gRNA ratio") +
  scale_colour_manual(values = c("#f9ab38", "#5672be")) + 
  facet_wrap(~ condition) +
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7),
        axis.line = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.8),
        legend.background = element_blank(),
        legend.direction = "horizontal",
        legend.key.size = unit(0.3, "cm"),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  guides(color = guide_legend(override.aes = list(size = 2, alpha = 1))) -> ratio_class


pdf("./Plots/Vero-variant_ratio-class.pdf",
    width = 11/2.54, height = 7/2.54)
print(ratio_class)
dev.off()
```

## Percentage super-permissive

```{r}
# Import data
FACS_df <- read_csv("./Data/Figure5/CoV-FISH-10_Vero-overivew-FACS.csv") %>%
  mutate(time = case_when(
    time == "02h" ~ "2 hpi",
    time == "06h" ~ "6 hpi",
    time == "08h" ~ "8 hpi",
    time == "24h" ~ "24 hpi"
  ))

# Create dataframe
FACS_bar <- FACS_df %>%
  filter(time == "6 hpi" | time == "8 hpi") %>%
  group_by(File, time, Virus, condition) %>%
  summarise(p.superinfected = sum(superinfected)/n() * 100) %>%
  ungroup()

# Statistics
FACS_bar %>% group_by(time, Virus, condition) %>% shapiro_test(p.superinfected) # Failed normality

FACS_bar %>% group_by(time, condition) %>% 
  wilcox_test(p.superinfected ~ Virus, p.adjust.method = "bonferroni") %>% add_significance()

# Plot
FACS_bar %>% 
  mutate(Virus = fct_rev(Virus)) %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = time, y = p.superinfected, fill = Virus)) +
  geom_bar(stat = "summary", fun.data = "mean_se",
           width = 0.65, position = position_dodge(0.8), alpha = 0.8) +
  geom_linerange(stat = "summary", fun.data = "mean_se", 
                 fun.args = list(mult = 1), size = 0.25,
                 position = position_dodge(0.8)) +
  scale_y_continuous(limits = c(0, 15)) +
  scale_fill_manual(values = c("#f9ab38", "#5672be")) + 
  labs(title = "% Super-permissive",
       x = "",
       y = "% cells per field of view") +
  facet_wrap(~ condition) +
  theme_classic(base_size = 7) +
  theme(plot.title       = element_text(hjust = 0.5),
        legend.title     = element_blank(),
        legend.position  = c(0.75, 0.85),
        legend.direction = "horizontal",
        axis.line        = element_blank(),
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5),
        legend.key.size  = unit(0.2, "cm")) -> sup_perm_variant

sup_perm_variant
  
# Export 
pdf("./Plots/FACS_Vero_bar-plot.pdf",
    width = 7.5/2.54, height = 4.5/2.54)
print(sup_perm_variant)
dev.off()

```






# SUPPLEMENTARY



## Vero FACS-like panel plot

```{r}
# * * * * * Import data
FACS_df <- read_csv("./Data/Figure5/CoV-FISH-10_Vero-overivew-FACS.csv") %>%
  mutate(time = case_when(
    time == "02h" ~ "2 hpi",
    time == "06h" ~ "6 hpi",
    time == "08h" ~ "8 hpi",
    time == "24h" ~ "24 hpi"
  ))

# * * * * * FACS plot
# Make annotation df
FACS_df_summary <- FACS_df %>% 
  group_by(time, Virus, condition) %>%
  summarise(Ch3.pool        = mean(Ch3.mean),
            Ch4.pool        = mean(Ch4.mean),
            p.superinfected = sum(superinfected)/n() * 100,
            cell.count      = n()) %>% 
  ungroup()

Vero_anno <- FACS_df_summary %>%
  mutate(y.pos = case_when(
    Virus == "Victoria" ~ 800,
    Virus == "B1.1.7" ~ 630,
    Virus == "Mock" ~ 500)) %>%
  mutate(p.superinfected = as.character(round(p.superinfected, 2))) %>%
  mutate(p.superinfected = paste0(p.superinfected, "%")) %>%
  mutate(Virus = fct_relevel(Virus, c("Victoria", "B1.1.7", "Mock"))) %>%
  mutate(condition = fct_rev(condition))

# Plot
FACS_df %>%
  filter(time != "24 hpi") %>% 
  mutate(Virus = fct_relevel(Virus, c("Victoria", "B1.1.7", "Mock"))) %>%
  arrange(Virus) %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = Ch3.mean, y = Ch4.mean, colour = Virus)) +
  geom_point(shape = 21, size = 0.6, alpha = 0.25, stroke = 0.25) +
  geom_vline(xintercept = 140, size = 0.1, alpha = 0.5) +
  labs(title    = "smFISH intensity per cell",
       x        = "ORF-N smFISH intensity",
       y        = "gRNA smFISH intensity") + 
  scale_x_log10(limits = c(1e2, 1e4),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_log10(limits = c(1e2, 1e3),
                labels = trans_format("log10", math_format(10^.x)),
                breaks = c(10^2, 10^2.5, 10^3)
                ) +
  scale_colour_manual(values = c("#f9ab38", "#5672be", "#d18975")) +
  facet_grid(condition ~ time) +
  theme_classic(base_size = 7) +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
  theme(plot.title = element_text(hjust = 0.5, size = 8),
        legend.position  = "bottom",
        legend.title = element_blank(),
        axis.line        = element_blank(), 
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5)) +
  geom_text(data = (Vero_anno %>% 
                      filter(time != "24 hpi")),
            aes(x = 200, y = y.pos, label = p.superinfected), 
            hjust = 0, show.legend = FALSE, size = 1.75) +
  guides(colour = guide_legend(override.aes = list(size = 2, alpha = 0.75, stroke = 0.6))) -> plot1

plot1

# Export 
pdf("./Plots/FACS_Vero_Full.pdf",
    width = 9/2.54, height = 7.4/2.54)
print(plot1)
dev.off()
```

## Bar plot for statistics

```{r}
# Import data
FACS_df <- read_csv("./Data/Figure5/CoV-FISH-10_Vero-overivew-FACS.csv") %>%
  mutate(time = case_when(
    time == "02h" ~ "2 hpi",
    time == "06h" ~ "6 hpi",
    time == "08h" ~ "8 hpi",
    time == "24h" ~ "24 hpi"
  ))

# Create dataframe
FACS_bar <- FACS_df %>%
  filter(time == "6 hpi" | time == "8 hpi") %>%
  group_by(File, time, Virus, condition) %>%
  summarise(p.superinfected = sum(superinfected)/n() * 100) %>%
  ungroup()

# Statistics
FACS_bar %>% group_by(time, Virus, condition) %>% shapiro_test(p.superinfected) # Failed normality

FACS_bar %>% group_by(time, condition) %>% 
  wilcox_test(p.superinfected ~ Virus, p.adjust.method = "bonferroni") %>% add_significance()

# Plot
FACS_bar %>% 
  mutate(Virus = fct_rev(Virus)) %>%
  mutate(condition = fct_rev(condition)) %>%
  ggplot(aes(x = time, y = p.superinfected, fill = Virus)) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) +
  geom_bar(stat = "summary", fun.data = "mean_se",
           width = 0.65, position = position_dodge(0.8), alpha = 0.8) +
  geom_linerange(stat = "summary", fun.data = "mean_sdl", 
                 fun.args = list(mult = 1), size = 0.25,
                 position = position_dodge(0.8)) +
  scale_y_continuous(limits = c(0, 15)) +
  scale_fill_manual(values = c("#f9ab38", "#5672be")) + 
  labs(title = "% Highly permissive",
       x = "",
       y = "% cells per field of view") +
  facet_wrap(~ condition, nrow = 2) +
  theme_classic(base_size = 7) +
  theme(plot.title       = element_text(hjust = 0.5, size = 8),
        legend.title     = element_blank(),
        legend.position  = "bottom",
        axis.line        = element_blank(),
        panel.border     = element_rect(colour = "black", fill = NA, size = 0.5),
        strip.background = element_rect(colour = "black", fill = NA, size = 0.5),
        legend.key.size  = unit(0.2, "cm")) -> plot2
  
# Export 
pdf("./Plots/FACS_Vero_bar-plot.pdf",
    width = 3.5/2.54, height = 6.9/2.54)
print(plot2)
dev.off()


```

## Vero B.1.1.7 8hpi super-permissive spatial randomness

```{r}
nndist_B117_Vero <- read_csv("./Data/Figure5/Vero_B117_8h_spatial_nn-distances.csv") %>%
  dplyr::select(c("Observed" = nn_distances_data, "Random" = nn_distances_sim)) %>%
  pivot_longer(everything(), names_to = "data_type", values_to = "nn_distance") %>%
  filter(!is.na(nn_distance)) %>%
  mutate(nn_distance = nn_distance * 0.65)

# Stats and parameters 
p_value <- nndist_B117_Vero %>% t_test(nn_distance ~ data_type) %>% add_significance() %>% pull(p)
p_value_label = paste0("p = ", p_value)

observed_mean <- nndist_B117_Vero %>% filter(data_type == "Observed") %>%
  pull(nn_distance) %>% mean() %>% round(0)
observed_mean_label = paste0("mean = ", observed_mean, " µm")

random_mean <- nndist_B117_Vero %>% filter(data_type == "Random") %>%
  pull(nn_distance) %>% mean() %>% round(0)
random_mean_label = paste0("mean = ", random_mean, " µm")


# Plot
ggplot() +
  geom_histogram(data = subset(nndist_B117_Vero, data_type == "Observed"),
                 aes(x = nn_distance, y = stat(ndensity), fill = data_type),
                 colour = "white", bins = 20, alpha = 1, size = 0.1) +
  geom_histogram(data = subset(nndist_B117_Vero, data_type == "Random"),
                 aes(x = nn_distance, y = stat(ndensity), fill = data_type),
                 bins = 50, alpha = 0.5) +
  scale_fill_manual(values = c("gray50", "#75b8d1")) + 
  scale_y_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2)) +
  labs(x = "Nearest neighbour \n distance (µm)",
       y = "Normalised count") + 
  theme_classic(base_size = 7) +
  theme(legend.title = element_blank(),
        axis.line = element_blank(),
        legend.position = c(0.7, 0.85),
        legend.key.size = unit(0.1, "cm"),
        legend.text = element_text(hjust = 0),
        legend.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        axis.text = element_text(size = 5)) +
  annotate("text", x = 325, y = 0.75, 
           label = observed_mean_label, colour = "gray30", size = 2, hjust = 0) +
  annotate("text", x = 325, y = 0.68, 
           label = random_mean_label, colour = "#75b8d1", size = 2, hjust = 0) +
  annotate("text", x = 325, y = 0.61, 
           label = p_value_label, colour = "gray30", size = 2, hjust = 0) -> spatial_b117_plot

spatial_b117_plot

pdf("./Plots/Spatial-randomness_b117.pdf",
    width = 1.47, height = 1.55)
print(spatial_b117_plot)
dev.off()
```


## Spatial distribution comparison of VIC vs. B.1.1.7 8h and 24h

```{r}
# * * * * * Import data

## 24hpi
nndist_VIC_24h <- read_csv("./Data/Figure5/A549_Vic_24h_spatial_nn-distances.csv") %>%
  dplyr::select(c("Observed" = nn_distances_data, "Random" = nn_distances_sim)) %>%
  pivot_longer(everything(), names_to = "data_type", values_to = "nn_distance") %>%
  filter(!is.na(nn_distance)) %>%
  mutate(nn_distance = nn_distance * 0.45)

nndist_B117_24h <- read_csv("./Data/Figure5/A549_B117_24h_spatial_nn-distances.csv") %>%
  dplyr::select(c("Observed" = nn_distances_data, "Random" = nn_distances_sim)) %>%
  pivot_longer(everything(), names_to = "data_type", values_to = "nn_distance") %>%
  filter(!is.na(nn_distance)) %>%
  mutate(nn_distance = nn_distance * 0.45)

## 8hpi
nndist_VIC_8h <- read_csv("./Data/Figure4/Spatial-randomness_A549_nn_distances.csv") %>%
  dplyr::select(c("Observed" = nn_distances_data, "Random" = nn_distances_sim)) %>%
  pivot_longer(everything(), names_to = "data_type", values_to = "nn_distance") %>%
  filter(!is.na(nn_distance)) %>%
  mutate(nn_distance = nn_distance * 0.45)

nndist_B117_8h <- read_csv("./Data/Figure5/A549_B117_8h_spatial_nn-distances.csv") %>%
  dplyr::select(c("Observed" = nn_distances_data, "Random" = nn_distances_sim)) %>%
  pivot_longer(everything(), names_to = "data_type", values_to = "nn_distance") %>%
  filter(!is.na(nn_distance)) %>%
  mutate(nn_distance = nn_distance * 0.65)

# * * * * * Define functions for stats/averaging/plotting

## Stats/Averaging
get_pvalue <- function(x){
  pvalue <- x %>% t_test(nn_distance ~ data_type) %>% add_significance() %>% pull(p)
  paste0("p = ", pvalue) %>% return()
}

get_mean_label <- function(x, y){
  observed_mean <- x %>% filter(data_type == y) %>%
  pull(nn_distance) %>% mean() %>% round(0)
  paste0("mean = ", observed_mean, " µm") %>% return()
}

get_rn <- function(df){
  variable_name <- deparse(substitute(df))
  total_area <- scan_area %>% filter(data == variable_name) %>% pull(area)
  n_images <- scan_area %>% filter(data == variable_name) %>% pull(n_images)
  nn_distance_vector <- df %>% filter(data_type == "Observed") %>% pull(nn_distance)
  Rn <- 2*(nn_distance_vector %>% mean()) / (sqrt(total_area*n_images*2/(length(nn_distance_vector))))
  Rn <- round(Rn, digits = 3)
  paste0("Rn = ", Rn) %>% return()
}

scan_area <- tibble(data = c("nndist_VIC_8h", "nndist_B117_8h", "nndist_VIC_24h", "nndist_B117_24h"),
                    area = c(1540000, 1210000, 15330000, 39430000),
                    n_images = c(8, 8, 2, 2))

get_rn(nndist_VIC_8h)
get_rn(nndist_B117_8h)
get_rn(nndist_VIC_24h)
get_rn(nndist_B117_24h)


## Plotting function
plot_nndistance <- function(df, ObsBin, RandBin){
  variable_name <- deparse(substitute(df))
  virus <- ifelse(str_detect(variable_name, "VIC"), "VIC", "B.1.1.7")
  hpi <- ifelse(str_detect(variable_name, "24h"), "24hpi", "8hpi")
  title <- paste0(virus, " ", hpi)
  colour <- ifelse(virus == "VIC", "#f9ab38", "#5672be")
  
  ggplot() +
  geom_histogram(data = subset(df, data_type == "Observed"),
                 aes(x = nn_distance, y = stat(ndensity), fill = data_type),
                 colour = "white", bins = ObsBin, alpha = 1, size = 0.1) +
  geom_histogram(data = subset(df, data_type == "Random"),
                 aes(x = nn_distance, y = stat(ndensity), fill = data_type),
                 bins = RandBin, alpha = 0.4) +
  scale_fill_manual(values = c("gray50", colour)) + 
  scale_y_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2)) +
  labs(title = title,
       x = "Nearest neighbour \n distance (µm)",
       y = "Normalised count") + 
  coord_cartesian(xlim = c(0, 800)) + 
  theme_classic(base_size = 7) +
  theme(plot.title = element_text(hjust = 0.5, size = 7, face = "bold"),
        legend.title = element_blank(),
        axis.line = element_blank(),
        legend.position = c(0.7, 0.85),
        legend.key.size = unit(0.1, "cm"),
        legend.text = element_text(hjust = 0),
        legend.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
        axis.text = element_text(size = 5)) +
  annotate("text", x = 325, y = 0.90, 
           label = get_mean_label(df, "Observed"), colour = "gray30", size = 2, hjust = 0) +
  annotate("text", x = 325, y = 0.83, 
           label = get_mean_label(df, "Random"), colour = colour, size = 2, hjust = 0) +
  annotate("text", x = 325, y = 0.76, 
           label = get_pvalue(df), colour = "gray30", size = 2, hjust = 0) +
  annotate("text", x = 325, y = 0.69, 
           label = get_rn(df), colour = "gray30", size = 2, hjust = 0)
}

# * * * * * Plot

(plot_nndistance(nndist_VIC_8h, 50, 100) + plot_nndistance(nndist_VIC_24h, 100, 500)) / 
  (plot_nndistance(nndist_B117_8h, 20, 100) + plot_nndistance(nndist_B117_24h, 85, 100)) + 
  plot_layout(guides = "collect") -> spatial_all_times

spatial_all_times

pdf("./Plots/Spatial-analysis-8hpi-24hpi.pdf",
    width = 5, height = 4.5)
print(spatial_all_times)
dev.off()




```












